Carbonate chemistry at Ny-Ålesund

### 2021-10-25 awipev-CO2.Rmd
Revised code for lm2 coefficients. Commented ghost code. drop_na ph_s_dur_temp_fb

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs(x="T 11 m", y="T FB ", color = "Months") 
print(p) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)

@@

**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor. All data are normalized at in situ temperature. The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018). lmodel2: Model II Regression. R package version 1.7-3. https://CRAN.R-project.org/package=lmodel2
=======
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
```

The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
>>>>>>> cb6a0f5891d0a4e43735bed5507c62760ae133cb

@@

p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet (both at FB temperature","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro", color = "Months")
p
```

@@

p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH spectro", y="pH seafet", color = "Months")
p
```

@@

  tidyr::drop_na(pco2_fb, at, sal_fb, temp_fb) %>% 

@@

  tidyr::drop_na(ct, at, sal_fb, temp_fb) %>% 

>>>>

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs(x="T 11 m", y="T FB ", color = "Months") 
print(p) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)

@@

**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor. All data are normalized at in situ temperature. The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018). lmodel2: Model II Regression. R package version 1.7-3. https://CRAN.R-project.org/package=lmodel2
<!-- ======= -->
<!--   theme(aspect.ratio=1,plot.title = element_text(size=7)) +  -->
<!--   coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+ -->
<!--   labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()   -->
<!-- ``` -->

The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
<!-- >>>>>>> cb6a0f5891d0a4e43735bed5507c62760ae133cb -->

@@

p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet (both at FB temperature","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro", color = "Months")
p
```

@@

p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH spectro", y="pH seafet", color = "Months")
p
```

@@

  tidyr::drop_na(ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 

@@

  tidyr::drop_na(ph_s_dur_temp_fb, ct, at, sal_fb, temp_fb) %>% 
